---
title: "FARS Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FARSpkg)
```

The functions in this package are designed to utilize data from the US National
Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS),
which is a nationwide census that provides the American public with yearly data 
concerning fatal injuries suffered in motor vehicle traffic crashes.

Data is provided only for the years 2013, 2014 and 2015.

The package consists of five (5) functions:

* **make_filename**  This function takes an input year and returns a file name
matching the FARS data files in the package.

* **fars_read**  This function loads the FARS data for the specific years of interest.

* **fars_read_years**  This function reads in the FARS data for a range of years 
(2003 - 2015)

* **fars_summarize_years**  This function produces a summary of the number of fatal
traffic accidents per month for the specific year of interest.

* **fars_map_state**  This function generates a map showing the location of fatal
traffic accidents for a given state and year, as requested by the user.

Further documentation can be found in the package documentation for each individual
function.
